Spectral Lags in Very High Energy Emission of Gamma Ray Bursts

### 2013-11-23 gammaRays.tex
Small phrasing changes in VHE bursts fraction section

Our final test is to calculate how much of the observable bursts can be observed in the very high energy range -- GeV and above.

To do so, we need to compute the number of bursts visible in a given energy range, which is the integral over space and jet directions:
\begin{align}
b\left(\omega_1,\omega_2\right) &= \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} 2\pi \sin\chi \dif\chi \nonumber\\
&\approx 2\pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} \chi \dif\chi = \pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_2\right)
\end{align}
Here $z_\text{max}\left(\omega_1,\omega_2\right)$ and $\chi_\text{max}\left(z,\omega_1,\omega_2\right)$ are the same values we used in the previous sections: the maximum redshift from which a burst can be observed, and the maximum off-axis angle with which the burst at redshift $z$ can be observed.

>>>>

Our final test is to calculate the fraction of the observable bursts which can be observed at the energies of GeV and above.

To do so, we need to compute the number of bursts visible in a given energy range, which is the integral over space and jet directions:
\begin{align}
b\left(\omega_1,\omega_2\right) &= \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} 2\pi \sin\chi \dif\chi \nonumber\\
&\approx 2\pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \int_0^{\chi_\text{max}\left(z,\omega_1,\omega_2\right)} \chi \dif\chi = \pi \int_0^{z_\text{max}\left(\omega_1,\omega_2\right)} \dif V\left(z\right) \rho\left(z\right) \chi^2_\text{max}\left(z,\omega_1,\omega_2\right)
\end{align}
Here $z_\text{max}\left(\omega_1,\omega_2\right)$ and $\chi_\text{max}\left(z,\omega_1,\omega_2\right)$ are the same values we used in the previous section: the maximum redshift from which a burst can be observed, and the maximum off-axis angle with which the burst at redshift $z$ can be observed.
